---
title: "Kruskal_analysis services questions"
author: "Ian Philips"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: styles_references_v1.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)

```



```{r datasetup,include=FALSE,message = FALSE,echo=FALSE}

require(tidyverse)
library(readxl)

library(knitr)
require(flextable)
require(viridis)
require(hrbrthemes)

require(rlang) # for !!sym()
require(HH) ##likert plot
require(descr)#produce a xtab
require(data.table)


#library(tidyverse)      # for data wrangling and visualization
#library(broom)          # for tidy test output
#library(ggpubr)         # for QQplot
#install.packages("conover.test")
#library(conover.test)   # for conover test




#dots to go up a directory from scripts to the r.proj dir
waves <- read_csv("../both_survey_waves_responses.csv")
dat_20 <- read_csv("../data2020_wrangled2021.csv")
dat_21 <- read_csv("../data2021.csv")


#question text and q number look ups
t_qtext_20 <- read_csv("../t_qtext_20.csv")
t_qtext_21 <- read_csv("../t_qtext_21.csv") 


#lookup table used to make comparisons between years 
lookup <- read_csv("../lookup_between_year_comparisons.csv") %>% filter(!is.na(comparison))

```




```{r}
#rename segments to remove hyphens  

dat_21$segment21[dat_21$segment21== "res_owner21"] <- "Resident ebike owner 21"
dat_21$segment21[dat_21$segment21== "visitor_ebike21"] <- "Visitor ebike owner 21"
dat_21$segment21[dat_21$segment21== "hirer21"] <- "Hirer 21"
dat_21$segment21[dat_21$segment21== "visitor_non_ebike21"] <- "Visitor non ebike 21"
dat_21$segment21[dat_21$segment21== "res_non_ebike21"] <- "Resident non ebike 21"


dat_20$segment[dat_20$segment== "hirer20"] <- "Hirer 20" 
dat_20$segment[dat_20$segment== "res_non_ebike20"] <- "Resident non ebike 20" 
dat_20$segment[dat_20$segment== "res_owner20"] <- "Resident ebike owner 20" 
dat_20$segment[dat_20$segment== "visitor_ebike20"] <- "Visitor ebike owner 20" 
dat_20$segment[dat_20$segment== "visitor_non_ebike20"] <- "Visitor non ebike 20" 

waves$segment21[waves$segment21== "res_owner21"] <- "Resident ebike owner 21"
waves$segment21[waves$segment21== "visitor_ebike21"] <- "Visitor ebike owner 21"
waves$segment21[waves$segment21== "hirer21"] <- "Hirer 21"
waves$segment21[waves$segment21== "visitor_non_ebike21"] <- "Visitor non ebike 21"
waves$segment21[waves$segment21== "res_non_ebike21"] <- "Resident non ebike 21"

waves$segment[waves$segment== "hirer20"] <- "Hirer 20" 
waves$segment[waves$segment== "res_non_ebike20"] <- "Resident non ebike 20" 
waves$segment[waves$segment== "res_owner20"] <- "Resident ebike owner 20" 
waves$segment[waves$segment== "visitor_ebike20"] <- "Visitor ebike owner 20" 
waves$segment[waves$segment== "visitor_non_ebike20"] <- "Visitor non ebike 20" 


```







```{r}

################# FUNCTIONS ######################


#-----builds a long format dataframe with columns segment chr, opinion ordered factor and likert integer of factor level
opiniondf_serv <- function(opinion_var = "Q19_2021_c_lickert_safety",
                            raw_var = "Q19_2021_c",
                            segment_var = "segment21",
                            segs = c("Resident ebike owner 21","Visitor ebike owner 21","Hirer 21"),
                            data_to_use = dat_21
                            ){

  require(rlang)

    #testing
   # opinion_var = raw.var21
   # raw_var = raw.var21
   # segment_var = "segment21"
   # segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21")
   # data_to_use = dat_21
   # ct_opinion_name = "parking"
   # plot_title = "testing parking storage"
   #                           print_the_ct = FALSE

  
 #makes a variaqble that we are going to tun into the "opinion variable"
  data_to_use <-  data_to_use %>% mutate(!!sym(opinion_var) := !!sym(raw_var))
 
 #assign dont know and na to neutral 
 data_to_use = data_to_use %>% 
    mutate(!!sym(opinion_var) := case_when(!!sym(opinion_var) == "don't know"  ~ "neutral",
                                           is.na(!!sym(opinion_var)) ~ "neutral",
                                           !!sym(opinion_var) == "very likely" ~"very likely",
                                           !!sym(opinion_var) == "quite likely" ~"quite likely",
                                           !!sym(opinion_var) == "neutral" ~"neutral",
                                           !!sym(opinion_var) ==  "quite unlikely"~ "quite unlikely",
                                           !!sym(opinion_var) == "very unlikely" ~ "very unlikely")
           
    )
  
  #subset the dataframe to just keep segment and opinion
  temp <- data_to_use %>%
    #filter(segment21 == "Resident ebike owner 21" | segment21 =="Visitor ebike owner 21"| segment21 =="Hirer 21") %>%
    filter(!!sym(segment_var) %in% segs) %>%
    #dplyr::select(segment = segment21, opinion =  Q19_2021_c_lickert_safety)
    dplyr::select(segment := !!sym(segment_var), opinion :=  !!sym(opinion_var))
  
  #glimpse(data_to_use)
  #make an ordered factor
  opinion_var = "opinion"  #had to add this 100923 didn't need it in the agree disagree questions
  temp = temp %>%
    mutate(!!sym(opinion_var) := factor(!!sym(opinion_var),levels =  c("very unlikely",
                                                                       "quite unlikely",
                                                                       "neutral",
                                                                       "quite likely",
                                                                       "very likely")
    )
    )

  

  #make a numeric value for the factor level 
  temp$likert <- as.integer(temp$opinion)
  
  return(temp)
  
}
 
##################### functions  200823 ############################## 

#takes the long format opinion dataframe (with columns segment and opinion) and produces a likert plot 
likert_from_opinion_serv <- function(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = "Riding an e-bike on the road in the\n Lake District feels safe most of the time"){
  
  
  #testing
  # input_long_df  = a
  # ct_opinion_name = ct.opinion.name
  # set_ref_zero =3
  # x_axis_percent = TRUE
  # plot_title = "Testing  bikes bla \n more text \n(cross sec)"

  
  input_long_df$opinion <-  as.character(input_long_df$opinion)
  
  
  # tally number of responses at each level
  temp3 <- input_long_df %>% group_by(segment,opinion) %>% tally() 
  #make into wide format
  temp3 <- temp3 %>%  pivot_wider(id_cols = "segment",
                                  names_from = "opinion", 
                                  values_from = "n"
                                  
  )
  
    #replace any na with 0 a count of no individuals with a particular 
  #likert score
  temp3 <- temp3 %>% replace(is.na(.), 0)
 #if there is an opinion category missing then sort it out
 temp3 <- temp3 %>% dplyr::select(any_of(
    c("very unlikely",
                                     "quite unlikely",
                                     "neutral",
                                     "quite likely",
                                     "very likely"
                        )
                                         )
                                   )
  
   #code to place 0 if there is a missing column
   if(!("very unlikely" %in% colnames(temp3))){
  temp3$'very unlikely' <- 0
  }
   
   if(!("quite unlikely" %in% colnames(temp3))){
  temp3$`quite unlikely` <- 0
  }
  
   if(!("neutral" %in% colnames(temp3))){
  temp3$neutral <- 0
  }
   
   if(!("quite likely" %in% colnames(temp3))){
  temp3$'quite likely' <- 0
  }
   
   if(!("very likely" %in% colnames(temp3))){
  temp3$'very likely' <- 0
  }
   
   
   
   #reorder columns
   temp3 <- temp3 %>% dplyr::select(
    c("very unlikely",
                                     "quite unlikely",
                                     "neutral",
                                     "quite likely",
                                     "very likely"
                        )
                                    )
   
  #make the Likert plot 
  lp <- likert(segment~.,temp3,
               ylab = "segment",xlab = "Percentage of respondents",
               as.percent = x_axis_percent,
               main=list(plot_title,cex=0.8),
               ReferenceZero=set_ref_zero,
               auto.key = list(columns = 2),
               rightAxis = FALSE, #don't show the row count totals on the right ,
               scales = list(y = list(cex = 0.8))
               )
  
  
  lp

}


##### ----------- Kruskal function  --------------- 
#performs kruskal wallis #dunn post hoc test too 


kruskal_func <- function(input_long_df  = a){
  
  #testing
  #input_long_df  = a
  
  #H0 - null hypothesis: all samples are the same
  #Halt - alternative hypothesis: at least one sample differs from at least one other


  kt <- kruskal.test(segment ~ likert, data =  input_long_df)
  
 
  # first_table <- input_long_df %>%
  #   mutate(rank = rank(likert)) %>%   # mutate means - create new column
  #   group_by(segment) %>%
  #   summarise(rank_sum  = sum(rank),
  #             rank_mean = mean(rank),
  #             mean_likert = mean(likert),
  #             median_likert = median(likert),
  #             n         = n() )
  

#-- Post hoc test ----   

dunn_out <- FSA::dunnTest(likert ~ segment,
              data = input_long_df,
              method="bh") 

dunn_out <- as.data.frame(dunn_out[["res"]]) # %>% filter(P.adj < 0.05)
dunn_out <- dunn_out %>%  filter(P.adj < 0.05)

to_output <- list(kt,dunn_out)  
return(to_output)

}


#### ---- compare same segment 2 years x section  ----------- 

#compares 1 segment in 2 different years.  
#we can uyse the same code R will see that there are only 2 groups and
#run the appropriate test 
compare_segs_across_years <- function(input_long_df  = a,
                                      seg20,seg21
                                      ){
  
  #testing
  # input_long_df  = a 
  # seg20 <- "female_Hirer 20"
  # seg21 <- "female_Hirer 21" 
  
  
  temp4 <-input_long_df %>%
    filter(segment == seg20|segment ==seg21)
  
  #H0 - null hypothesis: all samples are the same
  #Halt - alternative hypothesis: at least one sample differs from at least one other


  kt <- kruskal.test(segment ~ likert, data =  temp4)
  
  out_df <- data.frame(segment2020  = c(seg20),
                       segment2021 = c(seg21),
                       pvalue = kt$p.value)
  out_df <- out_df %>% filter(pvalue <=0.05)
 
 return(out_df)

  
  }



## ------ compare_segs_across_years_lookup using a look up to run several comparisons 
compare_segs_across_years_lookup <- function(df = a,
                                             lookup_table = lookup,
                                             to_compare = lookup$comparison#c("female_hirer","male_hirer")
                                             ){
 
  #testing
  # df = a
  # to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike")
  # lookup_table = lookup
  
  #filter to keep only the comparisions being run
  lu <- lookup_table %>% filter(comparison %in% to_compare)

  #make empty list
  compare_results <- list()  #initialize empty list
    
  #loop through the rows in lu 
  for(i in 1:nrow(lu)){
    #print(i)
  
    
    x <- compare_segs_across_years(input_long_df = df,
                              seg20 = lu$seg20[i],
                              seg21 = lu$seg21[i]
                              )
    compare_results[[length( compare_results)+1]] <- x
  }

   #convert the list into a dataframe
    compare_results <- plyr::ldply(compare_results, data.frame)
    return(compare_results)
}



#function that produces the net scores in likert tables 
#net being the difference in percent between some level 
#of agreement vs some level of disagreement
#this version of the function for the services questions with responses unliukely - likeley
net_agreement_serv <- function(inputdf,dopercent=TRUE){
  
  #testing
  #inputdf = a
    
    widea <- inputdf %>% group_by(segment,opinion) %>% tally() 
    
    widea <- widea %>%  pivot_wider(id_cols = "segment",
                                    names_from = "opinion", 
                                    values_from = "n"
                                    
    )
  
    widea <- widea %>% replace(is.na(.), 0)
   
  
  ##Next convert counts to %
  if(dopercent ==TRUE){
  widea$SUMCOL <- rowSums(widea[sapply(widea, is.numeric)], na.rm = TRUE)
  
  widea$`very unlikely` = round(100*(widea$`very unlikely`/widea$SUMCOL),0)
  widea$`quite unlikely` = round(100*(widea$`quite unlikely`/widea$SUMCOL),0)
  
  widea$`very likely` = round(100*(widea$`very likely`/widea$SUMCOL),0)
  widea$`quite likely` = round(100*(widea$`quite likely`/widea$SUMCOL),0)
  widea$neutral = round(100*(widea$neutral/widea$SUMCOL),0)
  
  widea$`net percent` <- round((
    (widea$`quite likely` +widea$`very likely`)-(widea$`quite unlikely` +widea$`very unlikely`)
  ),0)
  
  }
  
  return(widea)
 
}




wilcox_paired_waves_serv <- function(df = waves,
                                raw_var21 = raw.var21,
                                raw_var20 = raw.var20
){




  ##TESTING
  # df = waves
  # raw.var21 = "Q45_2021_a"
  # raw.var20 = "Q43a"
  # raw_var20 = raw.var20
  # raw_var21 = raw.var21
  

  data_to_use <- df %>% dplyr::select(segment21,segment, !!raw_var20,!!raw_var21, Q47_2021)
  data_to_use$segment21 <- paste0(data_to_use$Q47_2021, " ", data_to_use$segment21)
  data_to_use$segment <- paste0(data_to_use$Q47_2021, " ", data_to_use$segment)
  
#       data_to_use = dat_21 %>% filter(Q47_2021 == "female")
#a21f$segment <- paste0("Female ",a21f$segment)

  
  

  #assign dont know and na to neutral
  data_to_use = data_to_use %>%
    mutate(!!sym(raw_var20) := case_when(!!sym(raw_var20) == "don't know"  ~ "neutral",
                                         is.na(!!sym(raw_var20)) ~ "neutral",
                                         !!sym(raw_var20) == "very likely" ~"very likely",
                                         !!sym(raw_var20) == "quite likely" ~"quite likely",
                                         !!sym(raw_var20) == "neutral" ~"neutral",
                                         !!sym(raw_var20) ==  "quite unlikely"~ "quite unlikely",
                                         !!sym(raw_var20) == "very unlikely" ~ "very unlikely")

    )


  data_to_use = data_to_use %>%
    mutate(!!sym(raw_var21) := case_when(!!sym(raw_var21) == "don't know"  ~ "neutral",
                                         is.na(!!sym(raw_var21)) ~ "neutral",
                                         !!sym(raw_var21) == "very likely" ~"very likely",
                                         !!sym(raw_var21) == "quite likely" ~"quite likely",
                                         !!sym(raw_var21) == "neutral" ~"neutral",
                                         !!sym(raw_var21) ==  "quite unlikely"~ "quite unlikely",
                                         !!sym(raw_var21) == "very unlikely" ~ "very unlikely")


    )



  data_to_use = data_to_use %>% dplyr::select(segment21, segment20 = segment, opinion20 :=  !!sym(raw_var20),opinion21 :=  !!sym(raw_var21))

  #glimpse(data_to_use)

  #filter out any nas
  data_to_use = data_to_use[complete.cases(data_to_use),]

  #there are some panel respondents who were in a different segment in 2021 to 2020
  #e.g.  a person was a hirer in 2021 but in 2020 they visitied and didn't use an e-bike
  #or a person was a non-ebike owner in
  data_to_use$segment20 = paste0(data_to_use$segment21,"_20")



  #make a likert number for 2020 and 2021 opinions
  data_to_use = data_to_use%>%
    mutate(opinion21  = factor(opinion21,levels =  c("very unlikely",
                                                     "quite unlikely",
                                                                       "neutral",
                                                                       "quite likely",
                                                                       "very likely")
    )
    )

  #make a numeric value for the factor level
  data_to_use$likert21 <- as.integer(data_to_use$opinion21)


  data_to_use = data_to_use%>%
    mutate(opinion20  = factor(opinion20,levels =  c("very unlikely",
                                                                       "quite unlikely",
                                                                       "neutral",
                                                                       "quite likely",
                                                                       "very likely")
    )
    )

  #make a numeric value for the factor level
  data_to_use$likert20 <- as.integer(data_to_use$opinion20)




  #find all the segments in the waves data
  segments = data_to_use %>% group_by(segment21) %>% tally() %>% filter(!is.na(segment21))
  segment_var = segments$segment21 #makes a vector


  wt_results <- list()



  #this will be a loop
  for(i in 1:length(segment_var)){


    #subset the dataframe to just keep segment and opinion
    temp <- data_to_use %>%
      filter(segment21 == segment_var[i])
    #%>%
    #  dplyr::select(segment = segment21, opinion20 :=  !!sym(raw_var20),opinion21 :=  !!sym(raw_var21))
    #glimpse(temp)


    #make into long form
    temp2  <- temp %>% dplyr::select(seg = segment21, likert =likert21 )
    temp3 <- temp %>% dplyr::select(seg = segment20, likert =likert20 )

    temp4 <- rbind(temp2,temp3)

    #run the  two-samples paired Wilcoxon signed rank test  e.g. https://yury-zablotski.netlify.app/post/two-samples-wilcoxon-test/
    wt_l <- wilcox.test(data = temp4, likert~seg, paired = T, alternative = "less", conf.int = T, exact = F) %>% broom::tidy()
    wt_g <- wilcox.test(data = temp4, likert ~ seg, paired = T, alternative = "greater", conf.int = T, exact = F) %>% broom::tidy()

    wt <- rbind(wt_l,wt_g)
    wt$segment <- segment_var[i]

    #add results to list
    wt_results[[length(wt_results)+1]] <- wt

  }


  wt_results <- plyr::ldply(wt_results, data.frame)
  wt_results <- wt_results %>% filter(p.value < 0.05)
  regulartable(wt_results)

}










```

```{r}
###############################################################
######### ANALYSIS STARTS FROM HERE ###########################
###############################################################
```



# parking / storage "secure e-bike parking in towns and villages in the Lake District"

## NARRATIVE FOR PAPER 
The survey asked questions about how likely respondents would be to use particular facilities and services. There was strong support in both waves for secure e-bike storage (Figure 11).  There was a high net likelihood of using secure storage and parking amongst the e-bike using segments (Figure 11 & Figure PARK).  There were no significant differences within segments between 2020 and 2021 (cross section or panel).  In the 2020 cross sectional data Male hirers and male resident e-bike owners were significantly less likely to use parking and storage facilities than female resident owners.  There were no statistically significant differences in the panel data.  

## Cross Section analysis

```{r}
#name stuff 
raw.var21 = "Q44_2021_f" 
opinion.var21  = "Q44_2021_f"
raw.var20 = "Q42e" 
opinion.var20  = "Q42e"
ct.opinion.name  = "opinion"
plot.title = "How likeley are you to use \nsecure e-bike parking in towns and villages in the Lake District\n (cross section)"
```

```{r}
a21f <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "female")
                  )

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20"),
                  data_to_use =  dat_20 %>% filter(Q45 == "female")
                  
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "male")
                  )
                  


a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20"),
                  data_to_use =  dat_20 %>% filter(Q45 == "male")
                  
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```


```{r, warning = FALSE,message=FALSE}
#net values
rt = regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```



## run analysis on 2020 and 2021 cross section data



```{r,fig.dim = c(8, 5)}

likert_from_opinion_serv(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)



```




```{r}
## nb this runs on 2020 and 2021 data so mainly to test that code runs. 
#for comparisons use B and C 
# that way the comparison is 2020 segments with each other  (b) 
# then 2020 segments with each other (c)

 
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



### Compare each segment in 2020 with the same segment in 2021

```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                 to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <- regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```




## Run the plot on B(2020) and C(2021) separately to carry out within year comparisons



## B (2020)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```


```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## C (2021)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




## Waves analysis 

```{r}
plot.title = "How likeley are you to use secure e-bike parking\n in towns and villages in the Lake District\n(panel)"

a21f <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "female")
                  )

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20"),
                  data_to_use =  waves %>% filter(Q45 == "female")
                  
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "male")
                  )
                  


a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20"),
                  data_to_use =  waves %>% filter(Q45 == "male")
                  
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)



```



## run analysis on 2020 and 2021 PANEL data 


```{r, warning = FALSE,message=FALSE}
#net values
rt <- regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


```{r,fig.dim = c(8, 5)}
## make the likert chart
likert_from_opinion_serv(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 

```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                 to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <-regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```

## wilcoxon paired test on panel data (if table empty non significant)
```{r}

wilcox_paired_waves_serv()
```



## Run within year comparisons on the panel data

## B (2020) PANEL
```{r, fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



## C (2021) PANEL
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 
```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```


```{r}
################################ bike share scheme #############################
```




# Bike sharing "a scheme where you could pick up an e-bike in one place and drop it off in another (like a city bike share scheme)"

## NARRATIVE FOR PAPER 
Attitudes towards using a district-wide e-bike sharing scheme (Figure 12).  Support for a shared e-bike hire scheme is highest for hirers in 2020 but considerably lower in 2021, but it is not a statistically significant difference.  Visitors who do not own e-bikes have a net positive view towards using an e-bike share scheme.  E-bike owners have a low net likelihood of using shared e-bikes.  Male e-bike owners are statistically significantly less likely to use a shared e-bike scheme.      No segments were statistically significantly different between the two years in either the cross section or panel data.  

## Cross Section analysis

```{r}
#name stuff 
	
raw.var21 = "Q44_2021_a" 
opinion.var21  = "Q44_2021_a"
raw.var20 = "Q42a" 
opinion.var20  = "Q42a"

ct.opinion.name  = "opinion"
plot.title = "How likeley are you to use \na scheme where you could pick up an e-bike in one place\n and drop it off in another (like a city bike share scheme)\n (cross section)"
```

```{r}
a21f <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "female")
                  )

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                  data_to_use =  dat_20 %>% filter(Q45 == "female")
                  
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "male")
                  )
                  


a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = 
                    c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                  data_to_use =  dat_20 %>% filter(Q45 == "male")
                  
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```


```{r, warning = FALSE,message=FALSE}
#net values
rt = regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```



## run analysis on 2020 and 2021 cross section data



```{r,fig.dim = c(8, 6)}

likert_from_opinion_serv(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)



```




```{r}
 
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



### Compare each segment in 2020 with the same segment in 2021

```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                 to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <- regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```




## Run the plot on B(2020) and C(2021) separately to carry out within year comparisons



## B (2020)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```


```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## C (2021)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




## Waves analysis 

```{r}
plot.title = "How likeley are you to use \na scheme where you could pick up an e-bike in one place\n and drop it off in another (like a city bike share scheme)\n (panel)"

a21f <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "female")
                  )

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                  data_to_use =  waves %>% filter(Q45 == "female")
                  
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                  raw_var = raw.var21 ,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "male")
                  )
                  


a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                  raw_var = raw.var20,segment_var = "segment",
                  segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                  data_to_use =  waves %>% filter(Q45 == "male")
                  
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)



```



## run analysis on 2020 and 2021 PANEL data 


```{r, warning = FALSE,message=FALSE}
#net values
rt <- regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


```{r,fig.dim = c(8, 6)}
## make the likert chart
likert_from_opinion_serv(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 

```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                 to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <-regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## wilcoxon paired test on panel data (if table empty non significant)
```{r}

wilcox_paired_waves_serv()
```


## Run within year comparisons on the panel data

## B (2020) PANEL
```{r, fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



## C (2021) PANEL
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 
```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```


```{r}
############## ebike hire car restricted valley ############
```


# Figure 13 Respondents’ self-reported likelihood of using e-bike hire in a Lakeland Valley with restricted motor vehicle access.  



## NARRATIVE FOR PAPER 
How likely are you to use e-bike hire in a Lakeland valley which has restricted access to cars e.g. Langdale, Borrowdale

## Cross Section analysis

```{r}
#name stuff 


raw.var21 = "Q44_2021_e" 
opinion.var21  = "Q44_2021_e"
raw.var20 = "Q42d" 
opinion.var20  = "Q42d"

ct.opinion.name  = "opinion"
plot.title = "how likely are you to use e-bike hire in a Lakeland valley \nwhich has restricted access to cars \ne.g. Langdale, Borrowdale (cross section)"
```


```{r}
a21f <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = dat_21 %>% filter(Q47_2021 == "female")
)

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  dat_20 %>% filter(Q45 == "female")
                       
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = dat_21 %>% filter(Q47_2021 == "male")
)



a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = 
                         c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  dat_20 %>% filter(Q45 == "male")
                       
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```


```{r, warning = FALSE,message=FALSE}
#net values
rt = regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```



## run analysis on 2020 and 2021 cross section data



```{r,fig.dim = c(8, 6)}

likert_from_opinion_serv(input_long_df  = a,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```




```{r}

## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



### Compare each segment in 2020 with the same segment in 2021

```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                            to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <- regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```




## Run the plot on B(2020) and C(2021) separately to carry out within year comparisons



## B (2020)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```


```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## C (2021)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




## Waves analysis 

```{r}
plot.title = "how likely are you to use e-bike hire in a Lakeland valley \nwhich has restricted access to cars \ne.g. Langdale, Borrowdale (panel)"

a21f <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = waves %>% filter(Q47_2021 == "female")
)

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  waves %>% filter(Q45 == "female")
                       
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = waves %>% filter(Q47_2021 == "male")
)



a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  waves %>% filter(Q45 == "male")
                       
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)



```



## run analysis on 2020 and 2021 PANEL data 


```{r, warning = FALSE,message=FALSE}
#net values
rt <- regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


```{r,fig.dim = c(8, 6)}
## make the likert chart
likert_from_opinion_serv(input_long_df  = a,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                            to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <-regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## wilcoxon paired test on panel data (if table empty non significant)
```{r}

wilcox_paired_waves_serv()
```

## Run within year comparisons on the panel data

## B (2020) PANEL
```{r, fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



## C (2021) PANEL
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)

```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```


```{r}
#################### travel pass #######################
```







# "a daily or weekly pass which\n gives you e-bike hire together with use of all the buses\n, trains and boats in the Lake District National Park" 



## NARRATIVE FOR PAPER 
In the cross sectional data visitors are statistically more likely to use this service than residents.  Though the likert plot shows some similarities in the panel data, the differences are not statistically significant.  



## Cross Section analysis



```{r}
#name stuff 


raw.var21 = "Q44_2021_d" 
opinion.var21  = "Q44_2021_d"
raw.var20 = "Q42c" 
opinion.var20  = "Q42c"

ct.opinion.name  = "opinion"
plot.title = "how likely are you to use a daily or weekly pass which\n gives you e-bike hire together with use of all the buses\n, trains and boats in the Lake District National Park (cross section)"
```



```{r}
a21f <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = dat_21 %>% filter(Q47_2021 == "female")
)

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  dat_20 %>% filter(Q45 == "female")
                       
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = dat_21 %>% filter(Q47_2021 == "male")
)



a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = 
                         c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  dat_20 %>% filter(Q45 == "male")
                       
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```


```{r, warning = FALSE,message=FALSE}
#net values
rt = regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```



## run analysis on 2020 and 2021 cross section data



```{r,fig.dim = c(8, 7)}

likert_from_opinion_serv(input_long_df  = a,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```




```{r}

## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



### Compare each segment in 2020 with the same segment in 2021

```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                            to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <- regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```




## Run the plot on B(2020) and C(2021) separately to carry out within year comparisons



## B (2020)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```


```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## C (2021)
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




## Waves analysis 

```{r}
plot.title = "how likely are you to use a daily or weekly pass which\n gives you e-bike hire together with use of all the buses\n, trains and boats in the Lake District National Park (panel)"

a21f <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = waves %>% filter(Q47_2021 == "female")
)

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  waves %>% filter(Q45 == "female")
                       
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf_serv(opinion_var = opinion.var21,
                       raw_var = raw.var21 ,segment_var = "segment21",
                       segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21","Resident non ebike 21","Visitor non ebike 21"),
                       data_to_use = waves %>% filter(Q47_2021 == "male")
)



a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf_serv(opinion_var = raw.var20,
                       raw_var = raw.var20,segment_var = "segment",
                       segs = c("Visitor ebike owner 20","Hirer 20","Resident ebike owner 20","Resident non ebike 20","Visitor non ebike 20"),
                       data_to_use =  waves %>% filter(Q45 == "male")
                       
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)



```



## run analysis on 2020 and 2021 PANEL data 


```{r, warning = FALSE,message=FALSE}
#net values
rt <- regulartable(net_agreement_serv(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


```{r,fig.dim = c(8, 6)}
## make the likert chart
likert_from_opinion_serv(input_long_df  = a,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                            to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <-regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## wilcoxon paired test on panel data (if table empty non significant)
```{r}

wilcox_paired_waves_serv()
```

## Run within year comparisons on the panel data

## B (2020) PANEL
```{r, fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = b,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)



```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



## C (2021) PANEL
```{r,fig.asp= 0.8}
## make the likert chart
likert_from_opinion_serv(input_long_df  = c,
                         ct_opinion_name = ct.opinion.name,
                         set_ref_zero =3,
                         x_axis_percent = TRUE,
                         plot_title = plot.title)

```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




### notes 
the code is a bit scrappy in places.  

wilcoxon paired tests - sometimes run on segments that werent relevant to analysis - just easier to run code on all segments


the kruskall & dunn tests run on the data containing 2020 and 2021 data.  agian just relic of devleloping the code.   - for within year comparison of segments use "b" and "c" sections .  








