---
title: "Kruskal_analysis"
author: "Ian Philips"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: styles_references_v1.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)

```



```{r datasetup,include=FALSE,message = FALSE,echo=FALSE}

require(tidyverse)
library(readxl)

library(knitr)
require(flextable)
require(viridis)
require(hrbrthemes)

require(rlang) # for !!sym()
require(HH) ##likert plot
require(descr)#produce a xtab
require(data.table)


#library(tidyverse)      # for data wrangling and visualization
#library(broom)          # for tidy test output
#library(ggpubr)         # for QQplot
#install.packages("conover.test")
#library(conover.test)   # for conover test




#dots to go up a directory from scripts to the r.proj dir
waves <- read_csv("../both_survey_waves_responses.csv")
dat_20 <- read_csv("../data2020_wrangled2021.csv")
dat_21 <- read_csv("../data2021.csv")


#question text and q number look ups
t_qtext_20 <- read_csv("../t_qtext_20.csv")
t_qtext_21 <- read_csv("../t_qtext_21.csv") 


#lookup table used to make comparisons between years 
lookup <- read_csv("../lookup_between_year_comparisons.csv") %>% filter(!is.na(comparison))

```




```{r}
#rename segments to remove hyphens  

dat_21$segment21[dat_21$segment21== "res_owner21"] <- "Resident ebike owner 21"
dat_21$segment21[dat_21$segment21== "visitor_ebike21"] <- "Visitor ebike owner 21"
dat_21$segment21[dat_21$segment21== "hirer21"] <- "Hirer 21"
dat_21$segment21[dat_21$segment21== "visitor_non_ebike21"] <- "Visitor non ebike 21"
dat_21$segment21[dat_21$segment21== "res_non_ebike21"] <- "Resident non ebike 21"


dat_20$segment[dat_20$segment== "hirer20"] <- "Hirer 20" 
dat_20$segment[dat_20$segment== "res_non_ebike20"] <- "Resident non ebike 20" 
dat_20$segment[dat_20$segment== "res_owner20"] <- "Resident ebike owner 20" 
dat_20$segment[dat_20$segment== "visitor_ebike20"] <- "Visitor ebike owner 20" 
dat_20$segment[dat_20$segment== "visitor_non_ebike20"] <- "Visitor non ebike 20" 

waves$segment21[waves$segment21== "res_owner21"] <- "Resident ebike owner 21"
waves$segment21[waves$segment21== "visitor_ebike21"] <- "Visitor ebike owner 21"
waves$segment21[waves$segment21== "hirer21"] <- "Hirer 21"
waves$segment21[waves$segment21== "visitor_non_ebike21"] <- "Visitor non ebike 21"
waves$segment21[waves$segment21== "res_non_ebike21"] <- "Resident non ebike 21"

waves$segment[waves$segment== "hirer20"] <- "Hirer 20" 
waves$segment[waves$segment== "res_non_ebike20"] <- "Resident non ebike 20" 
waves$segment[waves$segment== "res_owner20"] <- "Resident ebike owner 20" 
waves$segment[waves$segment== "visitor_ebike20"] <- "Visitor ebike owner 20" 
waves$segment[waves$segment== "visitor_non_ebike20"] <- "Visitor non ebike 20" 


```







```{r}

################# FUNCTIONS ######################


#-----builds a long format dataframe with columns segment chr, opinion ordered factor and likert integer of factor level
opiniondf <- function(opinion_var = "Q19_2021_c_lickert_safety",
                            raw_var = "Q19_2021_c",
                            segment_var = "segment21",
                            segs = c("Resident ebike owner 21","Visitor ebike owner 21","Hirer 21"),
                            data_to_use = dat_21
                            ){

  require(rlang)

    #testing
  # opinion_var = "Q19_2021_c_lickert_safety"
  # raw_var = "Q19_2021_c"
  # segment_var = "segment21"
  # segs = c("Resident ebike owner 21","Visitor ebike owner 21","Hirer 21")
  # data_to_use = dat_21
  # ct_opinion_name = "safety"
  # plot_title = "Riding an e-bike on the road in the\n Lake District feels safe most of the time"
  #                           print_the_ct = FALSE

  
 #makes a variaqble that we are going to tun into the "opinion variable"
  data_to_use <-  data_to_use %>% mutate(!!sym(opinion_var) := !!sym(raw_var))
 
 #assign dont know and na to neutral 
  data_to_use = data_to_use %>% 
    mutate(!!sym(opinion_var) := case_when(!!sym(opinion_var) == "don't know"  ~ "neutral",
                                           is.na(!!sym(opinion_var)) ~ "neutral",
                                           !!sym(opinion_var) == "strongly disagree" ~"strongly disagree",
                                           !!sym(opinion_var) == "disagree" ~"disagree",
                                           !!sym(opinion_var) == "neutral" ~"neutral",
                                           !!sym(opinion_var) ==  "agree"~ "agree",
                                           !!sym(opinion_var) == "strongly agree" ~ "strongly agree")
           
    )
  
  #subset the dataframe to just keep segment and opinion
  temp <- data_to_use %>%
    #filter(segment21 == "Resident ebike owner 21" | segment21 =="Visitor ebike owner 21"| segment21 =="Hirer 21") %>%
    filter(!!sym(segment_var) %in% segs) %>%
    #dplyr::select(segment = segment21, opinion =  Q19_2021_c_lickert_safety)
    dplyr::select(segment := !!sym(segment_var), opinion :=  !!sym(opinion_var))
  
  #glimpse(data_to_use)
  #make an ordered factor 
  temp = temp %>% 
    mutate(opinion  = factor(opinion,levels =  c("strongly disagree",
                                                                       "disagree",
                                                                       "neutral",
                                                                       "agree",
                                                                       "strongly agree")
    )
    )

  #make a numeric value for the factor level 
  temp$likert <- as.integer(temp$opinion)
  
  return(temp)
  
}
 
##################### functions  200823 ############################## 

#takes the long format opinion dataframe (with columns segment and opinion) and produces a likert plot 
likert_from_opinion <- function(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = "Riding an e-bike on the road in the\n Lake District feels safe most of the time"){
  
  
  #testing
  # input_long_df  = b
  # ct_opinion_name = ct.opinion.name
  # set_ref_zero =3
  # x_axis_percent = TRUE
  # plot_title = "Riding an e-bike on the road in the\n Lake District feels safe most of the time"

  
  input_long_df$opinion <-  as.character(input_long_df$opinion)
  
  
  # tally number of responses at each level
  temp3 <- input_long_df %>% group_by(segment,opinion) %>% tally() 
  #make into wide format
  temp3 <- temp3 %>%  pivot_wider(id_cols = "segment",
                                  names_from = "opinion", 
                                  values_from = "n"
                                  
  )
  
    #replace any na with 0 a count of no individuals with a particular 
  #likert score
  temp3 <- temp3 %>% replace(is.na(.), 0)
 #if there is an opinion category missing then sort it out
 temp3 <- temp3 %>% dplyr::select(any_of(
    c("segment","strongly disagree","disagree","neutral","agree","strongly agree")
                                         )
                                   )
  
   #code to place 0 if there is a missing column
   if(!("strongly disagree" %in% colnames(temp3))){
  temp3$'strongly disagree' <- 0
  }
   
   if(!("disagree" %in% colnames(temp3))){
  temp3$disagree <- 0
  }
  
   if(!("neutral" %in% colnames(temp3))){
  temp3$neutral <- 0
  }
   
   if(!("agree" %in% colnames(temp3))){
  temp3$'agree' <- 0
  }
   
   if(!("strongly agree" %in% colnames(temp3))){
  temp3$'strongly agree' <- 0
  }
   
   
   
   #reorder columns
   temp3 <- temp3 %>% dplyr::select(
    c(segment,`strongly disagree`,disagree,neutral,agree,`strongly agree`)
                                    )
   
  #make the Likert plot 
  lp <- likert(segment~.,temp3,
               ylab = "segment",xlab = "Percentage of respondents",
               as.percent = x_axis_percent,
               main=list(plot_title,cex=0.8),
               ReferenceZero=set_ref_zero,
               auto.key = list(columns = 2),
               rightAxis = FALSE #don't show the row count totals on the right 
               )
  
  
  lp

}


##### ----------- Kruskal function  --------------- 
#performs kruskal wallis #dunn post hoc test too 
# should I add epsilon effect size too??  

kruskal_func <- function(input_long_df  = a){
  
  #testing
  #input_long_df  = a
  
  #H0 - null hypothesis: all samples are the same
  #Halt - alternative hypothesis: at least one sample differs from at least one other


  kt <- kruskal.test(segment ~ likert, data =  input_long_df)
  
 
  # first_table <- input_long_df %>%
  #   mutate(rank = rank(likert)) %>%   # mutate means - create new column
  #   group_by(segment) %>%
  #   summarise(rank_sum  = sum(rank),
  #             rank_mean = mean(rank),
  #             mean_likert = mean(likert),
  #             median_likert = median(likert),
  #             n         = n() )
  

#-- Post hoc test ----   
#pwt <- pairwise.wilcox.test(input_long_df$likert, input_long_df$segment)
#wmc(likert~segment,data = input_long_df) 

dunn_out <- FSA::dunnTest(likert ~ segment,
              data = input_long_df,
              method="bh") 

dunn_out <- as.data.frame(dunn_out[["res"]]) # %>% filter(P.adj < 0.05)
dunn_out <- dunn_out %>%  filter(P.adj < 0.05)

to_output <- list(kt,dunn_out)  
return(to_output)

}


#### ---- compare same segment 2 years x section  ----------- 

#compares 1 segment in 2 different years.  
#we can uyse the same code R will see that there are only 2 groups and
#run the appropriate test 
compare_segs_across_years <- function(input_long_df  = a,
                                      seg20,seg21
                                      ){
  
  #testing
  # input_long_df  = a 
  # seg20 <- "female_Hirer 20"
  # seg21 <- "female_Hirer 21" 
  
  
  temp4 <-input_long_df %>%
    filter(segment == seg20|segment ==seg21)
  
  #H0 - null hypothesis: all samples are the same
  #Halt - alternative hypothesis: at least one sample differs from at least one other


  kt <- kruskal.test(segment ~ likert, data =  temp4)
  
  out_df <- data.frame(segment2020  = c(seg20),
                       segment2021 = c(seg21),
                       pvalue = kt$p.value)
  out_df <- out_df %>% filter(pvalue <=0.05)
 
 return(out_df)

  
  }



## ------ compare_segs_across_years_lookup using a look up to run several comparisons 
compare_segs_across_years_lookup <- function(df = a,
                                             lookup_table = lookup,
                                             to_compare = lookup$comparison#c("female_hirer","male_hirer")
                                             ){
 
  #testing
  # df = a
  # to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike")
  # lookup_table = lookup
  
  #filter to keep only the comparisions being run
  lu <- lookup_table %>% filter(comparison %in% to_compare)

  #make empty list
  compare_results <- list()  #initialize empty list
    
  #loop through the rows in lu 
  for(i in 1:nrow(lu)){
    #print(i)
  
    
    x <- compare_segs_across_years(input_long_df = df,
                              seg20 = lu$seg20[i],
                              seg21 = lu$seg21[i]
                              )
    compare_results[[length( compare_results)+1]] <- x
  }

   #convert the list into a dataframe
    compare_results <- plyr::ldply(compare_results, data.frame)
    return(compare_results)
}



#function that produces the net scores in likert tables 
#net being the difference in percent between some level 
#of agreement vs some level of disagreement
net_agreement <- function(inputdf,dopercent=TRUE){
  
  #testing
  #inputdf = a
    
    widea <- inputdf %>% group_by(segment,opinion) %>% tally() 
    
    widea <- widea %>%  pivot_wider(id_cols = "segment",
                                    names_from = "opinion", 
                                    values_from = "n"
                                    
    )
  
    widea <- widea %>% replace(is.na(.), 0)
   
  
  ##Next convert counts to %
  if(dopercent ==TRUE){
  widea$SUMCOL <- rowSums(widea[sapply(widea, is.numeric)], na.rm = TRUE)
  
  widea$`strongly disagree` = round(100*(widea$`strongly disagree`/widea$SUMCOL),0)
  widea$disagree = round(100*(widea$disagree/widea$SUMCOL),0)
  
  widea$`strongly agree` = round(100*(widea$`strongly agree`/widea$SUMCOL),0)
  widea$agree = round(100*(widea$agree/widea$SUMCOL),0)
  widea$neutral = round(100*(widea$neutral/widea$SUMCOL),0)
  
  widea$`net percent` <- round((
    (widea$agree +widea$`strongly agree`)-(widea$disagree +widea$`strongly disagree`)
  ),0)
  
  }
  
  return(widea)
 
}





#### 

### WILCOXON PAIRED TEST ON THE PANEL DATA
## we run a mann whitney on the cross section data - mann whitney assumes independent not paired data
## the test does run on the panel data but the test isn't as powerful
## so we're running this Wilcoxon paired test on the panel data because here we know the data are the same person
#answering both waves . e.g.  a paired sample


#wilcox_paired_waves() #defaults are df = waves,#raw_var21 = raw.var21, #raw_var20 = raw.var20


wilcox_paired_waves <- function(df = waves,
                                raw_var21 = raw.var21,
                                raw_var20 = raw.var20
){




  ##TESTING
  # df = waves
  # raw.var21 = "Q45_2021_a"
  # raw.var20 = "Q43a"
  # raw_var20 = raw.var20
  # raw_var21 = raw.var21
  

  data_to_use <- df %>% dplyr::select(segment21,segment, !!raw_var20,!!raw_var21, Q47_2021)
  data_to_use$segment21 <- paste0(data_to_use$Q47_2021, " ", data_to_use$segment21)
  data_to_use$segment <- paste0(data_to_use$Q47_2021, " ", data_to_use$segment)
  
#       data_to_use = dat_21 %>% filter(Q47_2021 == "female")
#a21f$segment <- paste0("Female ",a21f$segment)

  
  

  #assign dont know and na to neutral
  data_to_use = data_to_use %>%
    mutate(!!sym(raw_var20) := case_when(!!sym(raw_var20) == "don't know"  ~ "neutral",
                                         is.na(!!sym(raw_var20)) ~ "neutral",
                                         !!sym(raw_var20) == "strongly disagree" ~"strongly disagree",
                                         !!sym(raw_var20) == "disagree" ~"disagree",
                                         !!sym(raw_var20) == "neutral" ~"neutral",
                                         !!sym(raw_var20) ==  "agree"~ "agree",
                                         !!sym(raw_var20) == "strongly agree" ~ "strongly agree")

    )


  data_to_use = data_to_use %>%
    mutate(!!sym(raw_var21) := case_when(!!sym(raw_var21) == "don't know"  ~ "neutral",
                                         is.na(!!sym(raw_var21)) ~ "neutral",
                                         !!sym(raw_var21) == "strongly disagree" ~"strongly disagree",
                                         !!sym(raw_var21) == "disagree" ~"disagree",
                                         !!sym(raw_var21) == "neutral" ~"neutral",
                                         !!sym(raw_var21) ==  "agree"~ "agree",
                                         !!sym(raw_var21) == "strongly agree" ~ "strongly agree")

    )



  data_to_use = data_to_use %>% dplyr::select(segment21, segment20 = segment, opinion20 :=  !!sym(raw_var20),opinion21 :=  !!sym(raw_var21))

  #glimpse(data_to_use)

  #filter out any nas
  data_to_use = data_to_use[complete.cases(data_to_use),]

  #there are some panel respondents who were in a different segment in 2021 to 2020
  #e.g.  a person was a hirer in 2021 but in 2020 they visitied and didn't use an e-bike
  #or a person was a non-ebike owner in
  data_to_use$segment20 = paste0(data_to_use$segment21,"_20")



  #make a likert number for 2020 and 2021 opinions
  data_to_use = data_to_use%>%
    mutate(opinion21  = factor(opinion21,levels =  c("strongly disagree",
                                                     "disagree",
                                                     "neutral",
                                                     "agree",
                                                     "strongly agree")
    )
    )

  #make a numeric value for the factor level
  data_to_use$likert21 <- as.integer(data_to_use$opinion21)


  data_to_use = data_to_use%>%
    mutate(opinion20  = factor(opinion20,levels =  c("strongly disagree",
                                                     "disagree",
                                                     "neutral",
                                                     "agree",
                                                     "strongly agree")
    )
    )

  #make a numeric value for the factor level
  data_to_use$likert20 <- as.integer(data_to_use$opinion20)




  #find all the segments in the waves data
  segments = data_to_use %>% group_by(segment21) %>% tally() %>% filter(!is.na(segment21))
  segment_var = segments$segment21 #makes a vector


  wt_results <- list()



  #this will be a loop
  for(i in 1:length(segment_var)){


    #subset the dataframe to just keep segment and opinion
    temp <- data_to_use %>%
      filter(segment21 == segment_var[i])
    #%>%
    #  dplyr::select(segment = segment21, opinion20 :=  !!sym(raw_var20),opinion21 :=  !!sym(raw_var21))
    #glimpse(temp)


    #make into long form
    temp2  <- temp %>% dplyr::select(seg = segment21, likert =likert21 )
    temp3 <- temp %>% dplyr::select(seg = segment20, likert =likert20 )

    temp4 <- rbind(temp2,temp3)

    #run the  two-samples paired Wilcoxon signed rank test  e.g. https://yury-zablotski.netlify.app/post/two-samples-wilcoxon-test/
    wt_l <- wilcox.test(data = temp4, likert~seg, paired = T, alternative = "less", conf.int = T, exact = F) %>% broom::tidy()
    wt_g <- wilcox.test(data = temp4, likert ~ seg, paired = T, alternative = "greater", conf.int = T, exact = F) %>% broom::tidy()

    wt <- rbind(wt_l,wt_g)
    wt$segment <- segment_var[i]

    #add results to list
    wt_results[[length(wt_results)+1]] <- wt

  }


  wt_results <- plyr::ldply(wt_results, data.frame)
  wt_results <- wt_results %>% filter(p.value < 0.05)
  regulartable(wt_results)

}









```

```{r}
###############################################################
######### ANALYSIS STARTS FROM HERE ###########################
###############################################################
```



# Safety "Riding a bike on the road in the \n Lake District is safe most of the time"


## Cross Section analysis

```{r}
#name stuff 
raw.var = "Q19_2021_c" 
opinion.var  = "Q19_2021_c"
ct.opinion.name  = "safety"
plot.title = "Riding a bike on the road in the \n Lake District is safe most of the time\n(cross section)"
```

```{r}
a21f <- opiniondf(opinion_var = "Q19_2021_c_lickert_safety",
                  raw_var = "Q19_2021_c",segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "female")
                  )

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf(opinion_var = "Q18c_likert_safety",
                  raw_var = "Q18c",segment_var = "segment",
                  segs = c("Hirer 20","Visitor ebike owner 20"),
                  data_to_use =  dat_20 %>% filter(Q45 == "female")
                  
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf(opinion_var = "Q19_2021_c_lickert_safety",
                  raw_var = "Q19_2021_c",segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "male")
                  
)

a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf(opinion_var = "Q18blikert_safety",
                  raw_var = "Q18b",segment_var = "segment",
                  segs = c("Hirer 20","Visitor ebike owner 20"),
                  data_to_use  = dat_20 %>% filter(Q45 == "male")
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```


```{r, warning = FALSE,message=FALSE}
#net values
rt = regulartable(net_agreement(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```



## run analysis on 2020 and 2021 cross section data
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)



```


```{r}
 
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



### Compare each segment in 2020 with the same segment in 2021

```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                 to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <- regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```




## Run the plot on B(2020) and C(2021) separately to carry out within year comparisons



## B (2020)
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = b,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```


```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## C (2021)
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = c,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




## Waves analysis (Safety)

```{r}
plot.title = "Riding a bike on the road in the \n Lake District is safe most of the time\n(panel)"

a21f <- opiniondf(opinion_var = "Q19_2021_c_lickert_safety",
                  raw_var = "Q19_2021_c",segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "female")
                  )

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf(opinion_var = "Q18c_likert_safety",
                  raw_var = "Q18c",segment_var = "segment",
                  segs = c("Hirer 20","Visitor ebike owner 20"),
                  data_to_use =  waves %>% filter(Q45 == "female")
                  
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf(opinion_var = "Q19_2021_c_lickert_safety",
                  raw_var = "Q19_2021_c",segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "male")
                  
)

a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf(opinion_var = "Q18blikert_safety",
                  raw_var = "Q18b",segment_var = "segment",
                  segs = c("Hirer 20","Visitor ebike owner 20"),
                  data_to_use  = waves %>% filter(Q45 == "male")
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```



## run analysis on 2020 and 2021 PANEL data safety question


```{r, warning = FALSE,message=FALSE}
#net values
rt <- regulartable(net_agreement(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


```{r}
## make the likert chart
likert_from_opinion(input_long_df  = a,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 

```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                 to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <-regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## wilcoxon paired test on panel data (if table empty non significant)
```{r}
### WILCOXON PAIRED TEST ON THE PANEL DATA
## we run a mann whitney on the cross section data - mann whitney assumes independent not paired data
## the test does run on the panel data but the test isn't as powerful
## so we're running this Wilcoxon paired test on the panel data because here we know the data are the same person
#answering both waves . e.g.  a paired sample


wilcox_paired_waves(df = waves,raw_var21 = "Q19_2021_c",raw_var20 = "Q18c") #defaults are df = waves,#raw_var21 = raw.var21, #raw_var20 = raw.var20

```

## Run within year comparisons on the panel data

## B (2020) PANEL
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = b,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



## C (2021) PANEL
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = c,
                           ct_opinion_name = ct.opinion.name,
                           set_ref_zero =3,
                           x_axis_percent = TRUE,
                           plot_title = plot.title)
 
```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```


```{r}
########################### HILLS ###########################
```




# Hills "I have ridden to places on the e-bike \n that I could not have ridden to on an ordinary bike"




## Cross Section analysis

```{r}
#name stuff 
raw.var = "Q19_2021_b" 
opinion.var  = "Q19_2021_b"
ct.opinion.name  = "hills"
plot.title = "I have ridden to places on the e-bike \n that I could not have ridden to on an ordinary bike (cross section)"
```

```{r}
a21f <- opiniondf(opinion_var = opinion.var,
                  raw_var = raw.var,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "female")
)

a21f$segment <- paste0("Female ",a21f$segment)



 a20f <- opiniondf(opinion_var = "Q18b",
                   raw_var = "Q18b",segment_var = "segment",
                   segs = c("Hirer 20","Visitor ebike owner 20","Resident ebike owner 20"),
                   data_to_use =  dat_20 %>% filter(Q45 == "female")

 )

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf(opinion_var = opinion.var,
                  raw_var = raw.var,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = dat_21 %>% filter(Q47_2021 == "male")
                  
)

a21m$segment <- paste0("Male ",a21m$segment)

 a20m <- opiniondf(opinion_var = "Q18b",
                   raw_var = "Q18b",segment_var = "segment",
                   segs = c("Hirer 20","Visitor ebike owner 20","Resident ebike owner 20"),
                   data_to_use  = dat_20 %>% filter(Q45 == "male")
 )
 
 a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```


```{r, warning = FALSE,message=FALSE}
#net values
rt = regulartable(net_agreement(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```



## run analysis on 2020 and 2021 cross section data
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = a,
                    ct_opinion_name = ct.opinion.name,
                    set_ref_zero =3,
                    x_axis_percent = TRUE,
                    plot_title = plot.title)



```


```{r}

## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



### not Comparing each segment in 2020 with the same segment in 2021 for waves because not enough data

```{r}

## not used not enough data in this section 

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.
#no "female_hirer", or no "male_hirer", "female_visitor_ebike", in one year of waves 
comp2yr <- compare_segs_across_years_lookup(df = a,
                                            to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <- regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```




## Run the plot on B(2020) and C(2021) separately to carry out within year comparisons



## B (2020)
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = b,
                    ct_opinion_name = ct.opinion.name,
                    set_ref_zero =3,
                    x_axis_percent = TRUE,
                    plot_title = plot.title)



```


```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


## C (2021)
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = c,
                    ct_opinion_name = ct.opinion.name,
                    set_ref_zero =3,
                    x_axis_percent = TRUE,
                    plot_title = plot.title)



```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




## Waves analysis (hills)

```{r}
plot.title = "I have ridden to places on the e-bike \n that I could not have ridden to on an ordinary bike (panel)"

a21f <- opiniondf(opinion_var = opinion.var,
                  raw_var = raw.var,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "female")
)

a21f$segment <- paste0("Female ",a21f$segment)



a20f <- opiniondf(opinion_var = "Q18b",
                  raw_var = "Q18b",segment_var = "segment",
                  segs = c("Hirer 20","Visitor ebike owner 20","Resident ebike owner 20"),
                  data_to_use =  waves %>% filter(Q45 == "female")
                  
)

a20f$segment <- paste0("Female ",a20f$segment)

a21m <- opiniondf(opinion_var = opinion.var,
                  raw_var = raw.var,segment_var = "segment21",
                  segs = c("Visitor ebike owner 21","Hirer 21","Resident ebike owner 21"),
                  data_to_use = waves %>% filter(Q47_2021 == "male")
                  
)

a21m$segment <- paste0("Male ",a21m$segment)

a20m <- opiniondf(opinion_var = "Q18b",
                  raw_var = "Q18b",segment_var = "segment",
                  segs = c("Hirer 20","Visitor ebike owner 20","Resident ebike owner 20"),
                  data_to_use  = waves %>% filter(Q45 == "male")
)

a20m$segment <- paste0("Male ",a20m$segment)

#glimpse(a21)
#glimpse(a20)

a <- rbind(a21f,a20f,a21m,a20m)
b <- rbind(a20f,a20m)
c <- rbind(a21f,a21m)


```



## run analysis on 2020 and 2021 PANEL data hills question


```{r, warning = FALSE,message=FALSE}
#net values
rt <- regulartable(net_agreement(a),cwidth = 1)
rt <- fontsize(rt,size = 9,part = "all")
rt

```


```{r}
## make the likert chart
likert_from_opinion(input_long_df  = a,
                    ct_opinion_name = ct.opinion.name,
                    set_ref_zero =3,
                    x_axis_percent = TRUE,
                    plot_title = plot.title)


```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = a)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



```{r}

#compare the segment in 2020 with the same segment in 2021
#adj P value < 0.05 means significant difference between years.  
comp2yr <- compare_segs_across_years_lookup(df = a,
                                            to_compare = c("female_hirer","male_hirer","female_visitor_ebike","male_visitor_ebike"))

rt <-regulartable(comp2yr %>% mutate_at(3:3, round, 3),cwidth = 2)
rt <- fontsize(rt,size = 9,part = "all")
rt

```



## wilcoxon paired test on panel data (if table empty non significant)
some segments may show sig diff here because question only asked of some segments in one of the years.  

```{r}
### WILCOXON PAIRED TEST ON THE PANEL DATA
## we run a mann whitney on the cross section data - mann whitney assumes independent not paired data
## the test does run on the panel data but the test isn't as powerful
## so we're running this Wilcoxon paired test on the panel data because here we know the data are the same person
#answering both waves . e.g.  a paired sample


wilcox_paired_waves(df = waves,raw_var21 = raw.var,raw_var20 = "Q18b") #defaults are df = waves,#raw_var21 = raw.var21, #raw_var20 = raw.var20

```

## Run within year comparisons on the panel data

## B (2020) PANEL
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = b,
                    ct_opinion_name = ct.opinion.name,
                    set_ref_zero =3,
                    x_axis_percent = TRUE,
                    plot_title = plot.title)



```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = b)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```



## C (2021) PANEL
```{r}
## make the likert chart
likert_from_opinion(input_long_df  = c,
                    ct_opinion_name = ct.opinion.name,
                    set_ref_zero =3,
                    x_axis_percent = TRUE,
                    plot_title = plot.title)

```

```{r}
## run kruskal wallis 
ktout <- kruskal_func(input_long_df  = c)
#print the test result 
#ktout[1]
#if the test result is significant then 
#this post hoc test (Dunn Test) can be used
#regulartable(as.data.frame(ktout[2]))

kt <- as.data.frame(ktout[2]) %>% dplyr::select(Comparison,P.adj) %>% mutate_at(2:2, round, 3)
#kt %>% dplyr::select(Comparison,P.adj)
rt = regulartable(kt,cwidth = 3)
rt <- fontsize(rt,size = 9,part = "all")
rt
```




